# Requirements

## Software requirements
The following software is required for the installation of the App:

* Windows 7 or higher
* Java SE Runtime Environment 7 or higher (<http://www.oracle.com/technetwork/java/javase/downloads/index.html>)
*	R v3.2.1 or higher (<https://cran.r-project.org/bin/windows/base/>)
*	RStudio v0.99.467 or higher (<https://www.rstudio.com/products/rstudio/download/>)
*	Rtools v.3.2 or higher (<https://cran.r-project.org/bin/windows/Rtools/>)
* A web-browser, such as Mozilla-Firefox, Chrome or Internet Explorer (v.11 or higher)

## R-Packages
The *import_App* requires a number of R-packages to run properly. The package is the fundamental unit of shareable code in R. A package bundles together code, data, documentation, etc. and is easy to share with others ([Wickham, 2017](#references)). They are available on-line and will be installed automatically by the App. The packages required by the App are:

```{r,  warning = FALSE, echo = FALSE}
cat(paste0(pkgs[[1]], collapse = "\n"))
```

These packages are saved in the following path:
```{r, echo=FALSE}
cat(RpkgsDir)
```
